### 2018-08-29 sections/data_presel.tex
fixing textual TLC comments

Single-electron and single-muon triggers with low $\pt$ threshold and lepton isolation requirements are combined in a logical OR 
with higher-threshold triggers without isolation requirements to give maximum efficiency. 
For muon triggers, the lowest $\pt$ threshold is 20 (26)~\gev\ in 2015 (2016), while the higher $\pt$ threshold is 50~\gev\ in both years. 
For electrons, triggers with a $\pt$ threshold of 24 (26)~\gev\ in 2015 (2016) and isolation requirements are used
along with triggers with a 60~\gev\ threshold and no isolation requirement, and with a 120 (140)~\gev\ threshold with looser identification criteria.
For ditau triggers, the $\pt$ threshold of the leading (trailing) $\tauhad$ candidate is 35 (25)~\gev\ with the medium identification required.
In both searches, events satisfying the trigger selection are required to have at least one primary vertex candidate.

>>>>

Single-electron and single-muon triggers with low $\pt$ threshold and lepton isolation requirements are combined in a logical OR 
with higher-threshold triggers without isolation requirements to give maximum efficiency. 
For muon triggers, the lowest $\pt$ threshold is 20 (26)~\gev\ in 2015 (2016), while the higher $\pt$ threshold is 50~\gev\ in both years. 
For electrons, triggers with a $\pt$ threshold of 24 (26)~\gev\ in 2015 (2016) and isolation requirements are used
along with triggers with a 60~\gev\ threshold and no isolation requirement, and with a 120 (140)~\gev\ threshold 
with looser identification criteria and no isolation requirement.
For ditau triggers, the $\pt$ threshold of the leading (trailing) $\tauhad$ candidate is 35 (25)~\gev\ with the medium identification required.
In both searches, events satisfying the trigger selection are required to have at least one primary vertex candidate.

### 2018-08-29 sections/objects.tex
fixing textual TLC comments

Hadronically decaying $\tau$-lepton ($\tauhad$) candidates are reconstructed from clusters in the calorimeters and
associated inner detector tracks~\cite{ATL-PHYS-PUB-2015-045}. Candidates are required to have either one or three associated tracks,
with a total charge of $\pm 1$. Candidates are required to have $\pt > 25~\gev$ and $|\eta|<2.5$, excluding the EM calorimeter's transition region.
A boosted decision tree (BDT) discriminant using calorimeter- and tracking-based variables is used to identify $\tauhad$ candidates and reject
jet backgrounds. Three working points labelled loose, medium and tight are defined, and correspond to different $\tauhad$ identification efficiency 
values, with the efficiency designed to be independent of $\pt$. The $\Htautau$ search uses the medium
working point for the nominal selection, while the loose working point is used for background estimation.
The medium working point has a combined reconstruction and identification efficiency of 55\% (40\%) for one (three)-prong $\tauhad$ 
decays~\cite{ATLAS-CONF-2017-029}, and an expected rejection factor against light-quark/gluon jets of 100~\cite{ATL-PHYS-PUB-2015-045}. 
Electrons that are reconstructed as one-prong $\tauhad$ candidates are removed via a BDT.
Any $\tauhad$ candidate that is also $b$-tagged is rejected.

>>>>

Hadronically decaying $\tau$-lepton ($\tauhad$) candidates are reconstructed from energy clusters in the calorimeters and
associated inner detector tracks~\cite{ATL-PHYS-PUB-2015-045}. Candidates are required to have either one or three associated tracks,
with a total charge of $\pm 1$. Candidates are required to have $\pt > 25~\gev$ and $|\eta|<2.5$, excluding the EM calorimeter's transition region.
A boosted decision tree (BDT) discriminant using calorimeter- and tracking-based variables is used to identify $\tauhad$ candidates and reject
jet backgrounds. Three working points labelled loose, medium and tight are defined, and correspond to different $\tauhad$ identification efficiency 
values, with the efficiency designed to be independent of $\pt$. The $\Htautau$ search uses the medium
working point for the nominal selection, while the loose working point is used for background estimation.
The medium working point has a combined reconstruction and identification efficiency of 55\% (40\%) for one (three)-prong $\tauhad$ 
decays~\cite{ATLAS-CONF-2017-029}, and an expected rejection factor against light-quark/gluon jets of 100~\cite{ATL-PHYS-PUB-2015-045}. 
Electrons that are reconstructed as one-prong $\tauhad$ candidates are removed via a BDT.
Any $\tauhad$ candidate that is also $b$-tagged is rejected.

### 2018-08-29 sections/signal_background_modeling.tex
fixing textual TLC comments

All simulated samples, except those produced with the {\sherpa}~\cite{Gleisberg:2008ta} event generator, 
utilise \textsc{EvtGen}~1.2.0~\cite{Lange:2001uf} to model the decays of heavy-flavour hadrons. 
To model the effects of pile-up, events from minimum-bias interactions are generated using the {\pythia}~8.186~\cite{Sjostrand:2007gs} 
event generator and overlaid onto the simulated hard-scatter events according to the luminosity profile of the recorded data. 
The generated events are processed through a simulation~\cite{Aad:2010ah} of the ATLAS detector geometry and response 
using \textsc{Geant4}~\cite{Agostinelli:2002hh}. A faster simulation, where the full \textsc{Geant4} simulation of
the calorimeter response is replaced by a detailed parameterisation of the shower shapes~\cite{FastCaloSim},
is adopted for some of the samples used to estimate systematic uncertainties.
Simulated events are processed through the same reconstruction software as the data, and corrections are applied so that the object identification 
efficiencies, energy scales and energy resolutions match those determined from data control samples.

>>>>

All generated samples, except those produced with the {\sherpa}~\cite{Gleisberg:2008ta} event generator, 
utilise \textsc{EvtGen}~1.2.0~\cite{Lange:2001uf} to model the decays of heavy-flavour hadrons. 
To model the effects of pile-up, events from minimum-bias interactions are generated using the {\pythia}~8.186~\cite{Sjostrand:2007gs} 
event generator and overlaid onto the simulated hard-scatter events according to the luminosity profile of the recorded data. 
The generated events are processed through a simulation~\cite{Aad:2010ah} of the ATLAS detector geometry and response 
using \textsc{Geant4}~\cite{Agostinelli:2002hh}. A faster simulation, where the full \textsc{Geant4} simulation of
the calorimeter response is replaced by a detailed parameterisation of the shower shapes~\cite{FastCaloSim},
is adopted for some of the samples used to estimate systematic uncertainties.
Simulated events are processed through the same reconstruction software as the data, and corrections are applied so that the object identification 
efficiencies, energy scales and energy resolutions match those determined from data control samples.
